Using VariantSpark to learn population structure from genomic profiles

### 2015-10-26 doc/publications/Recomb15/recomb15.tex
make two small changes -- why are the lines so long? hundreds of characters

%TODO other examples?
Determining a person's ethnicity has become important for medical applications, such as HLA allele genotyping from SNP information~\cite{Zheng2014}. Such clinical application are hence severely hampered for patients where accurate population association is unknown due to a diverse migrational background. Determining the population association from genomic information may provide vital insights for treatment and diagnostic in such cases.

>>>>

%TODO other examples?

Determining a person's ethnicity has become important for medical applications, such as HLA allele genotyping from SNP
information~\cite{Zheng2014}. Such clinical application are severely hampered for patients where accurate population
association is unknown due to a diverse migrational background. Determining the population association from genomic
information may provide vital insights for treatment and diagnostic in such cases.
